---
title: "Final Project"
author: "Mostafa Shad"
date: "January 30, 2016"
output: html_document
---

The following R commands are used to load the csv training data and create a training set and teting set:


```{r qplot, fig.width=4, fig.height=3, message=FALSE}
#Loading libraries and input data
library(ggplot2)
library(caret)
allData = read.csv("pml-training.csv") 

inTrain = createDataPartition(y=allData$classe, p=0.80, list=FALSE)

training = allData[inTrain,]
testing = allData[-inTrain,]
```

The input data should be pre processed in order to discard the missing and NA values with the following R code:

```{r}
preObj = preProcess(training, method="knnImpute")
```

To fit a model to these data, the following R code is used:
```{r}
modFit = train(classe ~ .,method = "rf",data = training)
```
Then, this model was evaluated by running it over the testing data and observe the confusion matrix:

```{r}
prediction = predict(modFit , newdata=testing)
prediction

confusionMatrix(prediction, testing$classe)
```

Since the results are acceptable, this model was executed over the main test set to see the output:

```{r}
mainTest  = read.csv("pml-testing.csv")
finalResult = predict(modFit , newdata=mainTest  )

finalResult
```